Abstractions for Multi-Sorted Substitutions

### 2023-09-18 paper/paper.tex
Update.

  As the amount of related work is rather large, we focus on work that
  is more closely related to ours and refer to other papers for the
  broader picture. In particular we cover abstractions for renamings
  and substitutions, comparable extrinsically typed approaches, but also
  intrinsically typed approaches that could be used as a basis for
  multi-sorted syntax, which as mentioned before is intrinsically typed
  in disguise.

>>>>

  As the amount of related work is rather large, we focus on work that
  is more closely related to ours and refer to other papers for the
  broader picture. In particular, we discuss abstractions for renamings
  and substitutions, comparable extrinsically typed approaches, but also
  intrinsically typed approaches that could be used as a basis for
  multi-sorted syntax, which as mentioned before is intrinsically typed
  in disguise.
